Predictors of frog survival following translocations - create dataset

### 2022-03-04 code/translocation_survival_createdata.Rmd
Add additional dataset creation steps

# Check that site_ids match expectation
frog_translocation %>% distinct(site_id)
frog_translocation %>% distinct(site_id, collect_siteid)

# Check if sex at collection matches sex on recapture

# Plot length x weight to check for outliers

```

@@

>>>>

# Check that site_ids match expectation
frog_translocation %>% distinct(site_id, collect_siteid)
```

@@

### Check data - third pass
```{r}
#### Connect to database
con = dbConnect(dbDriver("PostgreSQL"),
                host = Sys.getenv("host"), 
                port = Sys.getenv("port"), 
                dbname = Sys.getenv("dbname"),
                user = rstudioapi::askForPassword("user name"),
                password = rstudioapi::askForPassword("password")
               )
```
```{sql retrieve_capture_data, connection=con, output.var="frog_captures"}
select
	site_id,
	visit_date,
	survey_type,
	capture_life_stage,
	capture_animal_state,
	pit_tag_ref, 
	sex 
from visit
inner join survey on visit.id = visit_id
inner join capture_survey on survey.id = survey_id
inner join surveyor on surveyor.id = surveyor_id
where site_id in (70134, 70688, 70370, 70114, 70175, 70279, 70413, 71570, 71968, 72008, 72093, 72264, 72390, 72442, 72694, 70414, 70449, 70034, 70505, 72092, 70550, 70556, 70619, 70628, 70641, 74976, 72973) and 
	survey_type = 'cmr' and
	capture_animal_state != 'dead' 
```
```{r}
dbDisconnect(con)
rm(con)
```
```{r}
# Check if sex at collection matches sex on recapture
frog_captures %>% distinct(pit_tag_ref, sex) %>% count(pit_tag_ref, sex) %>% filter(n > 1)
frog_captures %>% distinct(pit_tag_ref, sex) %>% 
  rename(sexcapture = sex) %>% 
  inner_join(frog_translocation, by = "pit_tag_ref") %>% 
  filter(sex != sexcapture)
```
```{r}
# Plot length x weight to check for outliers
frog_translocation %>% ggplot(aes(x = length, y = weight)) +
  geom_point() +
  geom_smooth(method = lm)

frog_translocation %>% ggplot(aes(x = log10(length), y = log10(weight))) +
  geom_point() +
  geom_smooth(method = gam)

```
No obvious outliers.

### Clean data - third pass

```{r}
# Change sex at time of translocation based on subsequent recaptures
frog_translocation <- frog_translocation %>% 
  mutate(sex = replace(sex, pit_tag_ref == "900067000117464" & sex == "f", "m"),
         sex = replace(sex, pit_tag_ref == "982000365440205" & sex == "f", "m"),
         sex = replace(sex, pit_tag_ref == "900067000114152" & sex == "m", "f"))
```

### Add translocation order

```{r}
frog_translocation %>% 
  distinct(site_id, release_date) %>% 
  group_by(site_id) %>% 
  mutate(order = seq_len(n())) %>% 
  arrange(site_id, release_date) %>% 
  inner_join(frog_translocation, by = c("site_id", "release_date")) 
  ungroup() -> frog_translocation
```

### Extract day-of-year and year from date

```{r}
frog_translocation <- frog_translocation %>% 
  mutate(day = yday(release_date),
         year = year(release_date))
```

### Check for null values

```{r}
# Check for null values
frog_translocation %>% summarize(across(everything(), ~ sum(is.na(.))))
```

### Create final dataset

```{r}
frog_translocation <- frog_translocation %>% 
  rename(survival = median_survival,
         donor = collect_siteid,
         date = release_date) %>% 
  select(site_id, elevation, shore, date, day, year, order, pit_tag_ref, donor, sex, length, weight, bd_load, survival) 
```
